Untwisting the Tetrahelix (v0.7)

### 2017-02-28 doc/TetrahelixUntwist.tex
tweak

\begin{abstract}
  The Boerdijk--Coxeter helix (BC helix, or tetrahelix) is a
  face-to-face stack of regular tetrahedra.  Considering the edges of
  these tetrahedra as structural members, the resulting structure is attractive and
  inherently rigid, and therefore interesting to architects,
  mechanical engineers, and robotocists.  A formula that matches the
  visually apparent helices forming the outer rails of the tetrahelix
  is derived which is convenient for designers.  This formula defines
  the vertices of tetrahelices of varying radius, pitch, and
  curvature, with the BC helix as a special case.  An addtional
  special case is of that of $0$ curvature or rail angle, which
  generates a \emph{tetrabeam}.  A particular choice of paramaters
  defines a novel object, the minimax optimal member length-difference
  tetrabeam, the \emph{equitetrabeam}.  A formula for computing the
  radius and z-axis travel that gives an optimal minimax tetrahelix
  for any rail angle between $0$ and $\rho_{bc}$ is given, thus
  defining a continuum of tetrahelices terminated by the equitetrabeam
  and BC helix. Numerically finding the rail angle from the equation for
  pitch allows optimal tetrahelices of any pitch to be designed.
  An interactive tool for such design and experimentation is provided.
  Utility and use for static and variable geometry
  truss/space frame design and robotics based on the are discussed.
\end{abstract}

@@

\begin{align*}
  1 &=  \sqrt{\frac{1}{9}  + r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
  r_{opt} &= \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }} \numberthis  \label{eqrhoopt} \\
\end{align*}

@@

\begin{align*}
  d_{opt}^2 &= 1 - 4 \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }}^2 (\sin{ \rho / 2})^2   \\
  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
  d_{opt}^2 &= 1 - \frac{16(\sin{ \rho / 2})^2}{9 ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + cos(\rho)+ 8 }    \\
  d_{opt}^2 &= 1 - \frac{16 sin^2(\rho / 2) }{ cos(\rho) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
    d_{opt} &= \sqrt{1 - \frac{16 sin^2(\rho / 2) }{ cos(\rho) + 9( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
\end{align*}

@@

Create working toolkit for desin/exploration.

>>>>

\begin{abstract}
  The Boerdijk--Coxeter helix (BC helix, or tetrahelix) is a
  face-to-face stack of regular tetrahedra.  Considering the edges of
  these tetrahedra as structural members, the resulting structure is attractive and
  inherently rigid, and therefore interesting to architects,
  mechanical engineers, and robotocists.  A formula that matches the
  visually apparent helices forming the outer rails of the tetrahelix
  is derived which is convenient for designers.  This formula defines
  the vertices of tetrahelices of varying radius, pitch, and
  curvature, with the BC helix as a special case.  An addtional
  special case is of that of $0$ curvature or rail angle, which
  generates a \emph{tetrabeam}.  A particular choice of paramaters
  defines a novel object, the minimax optimal member length-difference
  tetrabeam, the \emph{equitetrabeam}.  A formula for computing the
  radius and z-axis travel that gives an optimal minimax tetrahelix
  for any rail angle between $0$ and $\rho_{bc}$ is given, thus
  defining a continuum of tetrahelices terminated by the equitetrabeam
  and BC helix. Numerically finding the rail angle from the equation for
  pitch allows optimal tetrahelices of any pitch to be designed. 
  An interactive tool for such design and experimentation is provided.
  A formula
  for the inradius is given.
  Utility and use for static and variable geometry
  truss/space frame design and robotics based on the are discussed.
\end{abstract}

@@

\begin{align*}
  1 &=  \sqrt{\frac{1}{9}  + r_{opt}^2(-\frac{4 (\sin^2( \rho / 2))}{9} + \sin^2(\rho/3+ \frac{2\pi}{3})  + (1 - \cos(\rho/3 + \frac{2\pi}{3}))^2)} \\
  r_{opt} &= \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }} \numberthis  \label{eqrhoopt} \\
\end{align*}

@@

\begin{align*}
  d_{opt}^2 &= 1 - 4 \frac{2}{\sqrt{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }}^2 (\sin{ \rho / 2})^2   \\
  d_{opt}^2 &= 1 - 4 \frac{4(\sin{ \rho / 2})^2}{\frac{9}{2} \cdot ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
  d_{opt}^2 &= 1 - \frac{16(\sin{ \rho / 2})^2}{9 ( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + \cos(\rho)+ 8 }    \\
  d_{opt}^2 &= 1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }   \\
    d_{opt} &= \sqrt{1 - \frac{16 \sin^2(\rho / 2) }{ \cos(\rho) + 9( \sqrt{3} \sin(\rho/3) + \cos(\rho/3)) + 8 }}    \numberthis  \label{dopt}  \\      
\end{align*}

@@

Create working toolkit for design/exploration.
